Titulo

### 2015-02-10 RotacionOutFlows/Paper/ms.tex
Intro first draft, still missing references and additional info

\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero, Juan N. Garavito-Camargo}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{mc.remolina197@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}
\email{jn.garavito57@uniandes.edu.co}

\keywords{Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}

@@

The Lyman-Alpha emission line is the spectral line produced when an electron goes from the second energy level to the first, loosing energy and emitting it as light. When this energy decays are seen in Hydrogen atoms, the wavelength of the \lya line is 121.567 nm. The detection of this emission line is a main tecnique in extragalactic astronomy because galaxies with a strong emission of this (called Lyman Alpha Emitters - LAEs) are used to study the evolution of the universe in big scale. \\

LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material. Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations. \\

Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\

---------------------------------------------------------------------\\
MISSING: What has been done related to this?\\
-----------------------------------------------------------------------\\

As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emitted from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\

In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\

After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
center. That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity. Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\

As there is a lot of empty space inside the shell, it acts as a reflector of photons. This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping. However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous. \\

>>>>

\author{ Maria Camila Remolina-Gutierrez, Jaime E. Forero-Romero \& Juan N. Garavito-Camargo}
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{mc.remolina197@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}
\email{jn.garavito57@uniandes.edu.co}

\keywords{Galaxies: high-redshift, Lyman Alpha Emission, Galaxy Rotation, Galaxy Outflows ....MISSING....}

@@

In 1967 \cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Ostlin14}  ,  become a very important tool to 
explore the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
line is redshifted into the optical regime. it is specially useful to study the 
properties of the high redshift Universe, such as the large scale structure.
and new projects are beeing planned for the near future $\cite{}$.

A variety of Astrophysical problems can be studied using LAEs; clustering
of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
properties and cosmological reionization among others. This motivates to study in 
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be modeled.
however the resonant nature of the lines makea this a challenging task. 
Neufeld et 90 the outcoming spectra of galaxies through static mediums 
Recent hydrodynamical simulations have been explored the properties of the IGM/ISM 
in large scale simulations, while some others have studied detailed galaxies. 
On the other hand RT computations have been in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

As many previous studies have shown outflows are present in LAEs (\textbf{References}),
the outflows are mainly a consecuence of the intergalactic medium (IGM) being ejected 
from the galaxy due to supernova explotions.
However rotation should also be present in this galaxies. The joint effect of the two 
above properties should have a direct effect on the morphology of the \lya line.

This effect is the motivation of this paper in which we combine the effect of rotation 
follow by an outflow. We proposed a simplyfied model in which the galaxy is modeled
as an sphere, with an homogeneous mixture of dust and hydrogen at a constant temperature
and undergoing solid-body rotation.

The solid-body rotation does not induce any spatial anisotropy in the integrated line flux, 
the escape fraction or in the average number of scatterings. This symmetry allows 
to the creation of an analytic approximation for the galaxy spectrum 
proposed, see \cite{Garavito14} for details. In this model the optical depth $\tau_{H}$, the 
rotation velocity $V_{max}$ and the inclination angle $\theta$ are free parameters.

The outcoming spectra of the rotating galaxy is then affected by a symmetric thin shell of expanding
gas at a constant velocity following the model proposed by \cite{2014arXiv1404.2958V, Orsi12}.

This paper is structured as follows. In \S \ref{sec:theo} we explain in detail the model of rotation
and outflow that we use as well of our joint model (Rotation \& Outflow). In \S \ref{sec:results} we present
the results of our model. In \S \ref{sec:discussion} we compare our results with 
recent observations of LAEs with special attention of those morphologies that present
features of galaxy rotation and outflows. In the latest section we present our 
conclutions.

%LAEs are young and far away galaxies with most of its matter composed by Hydrogen atoms, being the rest heavier elements, like Iron, produced by growing stars burning their material. Then, this spectral line tells very important information about the galaxy, most of it actually, which creates a motivation to find a way to model the \lya line according to certain free parameters that vary from a galaxy to another and that can be obtained from observations. \\

%Our purpose in this paper is then to make a theoretical model, based on radiative transfer simulations, that use MonteCarlo
%computational methods to emulate how the line profile is going to come out of the galaxy if it is rotating and has a surrounding
%outflow, both of this phenomena characterized by key parameters that are going to be described further on the paper. \\

%As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emitted from a central distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\

%In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average
%number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression
%helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\

%After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the
%center. That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity. Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\

%As there is a lot of empty space inside the shell, it acts as a reflector of photons. This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping. However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous. \\
